---
title: "R Markdown Presentation and Plotly"
author: "Dr -A"
date: "11/06/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
	message = FALSE,
	warning = FALSE,
	cache = TRUE,
	tidy = TRUE,
	tidy.opts = list(width.cutoff = 60))
```

## Overview:{.smaller}

This assignment consist task of creating a web page presentation using R Markdown that features a plot created with ploty.
The page than need to be hosted on either GitHub, Rpubs or Neocities.

 Requirements:

 * The webpage must contain the date that I created the document on, and 
 it must contain a plot created with Plotly, and little bit of creativity.
 
## In this assignment I will use Iris and diamond data to plot.{.smaller}

Load Dataset and Libraries:{.smaller}

```{r}
library(plotly)
data("iris")
data("diamonds")

```

## Data Information for Iris{.smaller}

```{r}
summary(iris)
```

## Data Indormation for Diamonds:{.smaller}
```{r}
summary(diamonds)
```


## Plot1: {.smaller}
```{r}
plot_ly(data = iris, x = ~Sepal.Length, y = ~Petal.Length, color = iris$Species)

```

### Hover over text plot with diamond data.{.smaller}
```{r, echo= FALSE}
dia_mond <- diamonds[sample(nrow(diamonds), 500), ]
```

## Figure{.smaller}
```{r}
plot_ly(data = dia_mond, x = ~carat, y = ~price, color = ~carat,
        text = ~paste("Price:", price, "$<br>Cut:", cut), size = ~carat)

```




